---
title: "Leave one out (LOO) means of student data"
author: "Stef Meliss"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
# empty work space
rm(list = ls())

# define directory
dir <- getwd()
dir <- gsub("/00_explore", "", dir)

# load libraries
library(kableExtra)
library(ggplot2)
library(dplyr)

# load in functions
devtools::source_url("https://github.com/stefaniemeliss/Global_Teaching_InSights/blob/main/functions.R?raw=TRUE")

```

```{r, include=F}
stud <- read.csv(file.path(dir, "data_raw", "GTI-Student-Data.csv"))
group <- "COUNTRY"
```


Contents  

[Test scores](#test)  
[Self-concept in mathmatics](#selfcon)  
[Interest in mathmatics](#int)  
[Self-efficacy](#effi)  
[Opportunities to Learn](#otl)  


```{r working_chunk, echo=FALSE, eval=F}


# compute LOO mean #

# create tmp df with relevant columns
tmp <- stud[, c("S_ID", "T_ID", "COUNTRY", dv)]

new_var <- paste0("LOO_", dv)

# add LOO mean
tmp <- tmp %>% 
  group_by(T_ID) %>%
  # compute leave one out mean
  mutate(new_var = (sum(get(dv), na.rm = T) - get(dv))/(n() - sum(is.na(get(dv))) - 1),
         n = (n() - sum(is.na(get(dv))) - 1))

names(tmp)[names(tmp) == "new_var"] <- new_var

# make df (currently tbl)
tmp <- as.data.frame(tmp)


# generate and print descriptive tables to markdown
table_desc(data = tmp,
           group_var = group,
           dep_var = new_var)


# create plots #

# input vars
x_var = dv
y_var = new_var
x_lab <- paste(label, "RAW")
y_lab <- paste(label, "LOO")

# scatterplot all countries #
main <- "Scatterplot (jittered) showing data for all countries"
# create basic plot
plt_all <- plot_scatter_jitter(data = tmp,
                        xvar = x_var,
                        yvar = y_var,
                        xlab = x_lab,
                        ylab = y_lab,
                        title = main)
# print plot
plt_all

# scatterplot for each country #
main <- "Scatterplot (jittered) showing data for each country"

# create basic plot
plt_grp <- plot_scatter_jitter(data = tmp,
                        xvar = x_var,
                        yvar = y_var,
                        xlab = x_lab,
                        ylab = y_lab,
                        title = main)
# make nicer
plt_grp <- plt_grp + 
  facet_wrap(. ~ get(group), ncol = 2)
# print plot
plt_grp
```


# Test scores {#test}

### Pre-test

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "STA_IRTSCORE"
label <- "IRT score pre-test"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "STA_PROPCORRECTSCORE"
label <- "Proportion of correct answers pre-test"

<<working_chunk>>

```

### Post-test

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "STB_IRTSCORE"
label <- "IRT score post-test"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "STB_PROPCORRECTSCORE"
label <- "Proportion of correct answers post-test"

<<working_chunk>>

```


# Self-concept in mathmatics {#selfcon}

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SA_SELFCON"
label <- "Self-concept pre"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_SELFCON"
label <- "Self-concept post"

<<working_chunk>>

```

# Interest in mathmatics {#int}


```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "PRE_PINT"
label <- "Personal interest pre (previous teacher)"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SA_PINT_CURR"
label <- "Personal interest pre (current teacher)"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "POST_PINT"
label <- "Personal interest post"

<<working_chunk>>

```


# Self-efficacy {#effi}

### General self-efficacy  

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "PRE_GENSELFEFF"
label <- "General self-efficacy pre (previous teacher)"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SA_GENSELFEFF_CURR"
label <- "General self-efficacy pre (current teacher)"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "POST_GENSELFEFF"
label <- "General self-efficacy post"

<<working_chunk>>

```

### Self-efficacy with mathematical tasks

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SA_EFFICACY"
label <- "Task-specific self-efficacy pre"

<<working_chunk>>

```

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_EFFICACY"
label <- "Task-specific self-efficacy post"

<<working_chunk>>

```

# Opportunities to learn {#otl}

### Student perception of opportunity to use quadratic functions

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_OTL_FUNCTION"
label <- "OTL Functions"

<<working_chunk>>

```

### Student perception of opportunity to learn algebraic operations

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_OTL_ALGEBRA"
label <- "OTL Algebra"

<<working_chunk>>

```


### Student perception of opportunity to learn reasoning about different types of quadratic equations

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_OTL_REASON"
label <- "OTL Reasoning"

<<working_chunk>>

```

### Student perception of opportunity to apply quadratic equations to real world contexts

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define DV and label
dv <- "SB_OTL_APPLIED"
label <- "OTL Application"

<<working_chunk>>

```


```{r, include=F}
tmp <- stud[, grep("SQB07E", names(stud))]

# replace all 9999 with NA
tmp <- tmp %>%
  mutate(across(where(is.integer), ~na_if(., 9999)))

# recode values
tmp2 <- tmp %>%
  # replace all 9999 with NA
  mutate(across(where(is.integer), ~na_if(., 9999))) %>%
  # recode all items (previously coded as 1 = YES and 2 = NO) to 1 = YES and 0 = NO
  mutate(across(where(is.integer), ~recode(., `1` = 1, `2` = 0)))

# compute scales #

# SB_OTL_FUNCTION: Scale measuring student perception of opportunity to use quadratic functions. 


# SB_OTL_ALGEBRA: Scale measuring student perception of opportunity to learn algebraic operations. 

# SB_OTL_REASON: Scale measuring student perception of opportunity to learn reasoning about different types of quadratic equations. 

# SB_OTL_APPLIED	Scale measuring student perception of opportunity to apply quadratic equations to real world contexts.

```

