---
title: "Measurement invariance (MI): Non-cognitive Student Outcomes [1 COUNTRY REMOVED]"
author: "Stef Meliss"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
# empty work space
rm(list = ls())

# define directory
dir <- getwd()
dir <- gsub("/00_explore", "", dir)

# load libraries
library(kableExtra)
library(dplyr)
library(ggplot2)

library(mirt)
library(ggmirt)

library(plotly)

library(lavaan)
library(semPlot)
library(semptools)
library(semTools)

# load in functions
devtools::source_url("https://github.com/stefaniemeliss/Global_Teaching_InSights/blob/main/functions.R?raw=TRUE")

# read in data
all_data <- read.csv(file.path(dir, "data_raw", "GTI-Student-Data.csv"))

# replace all 9999 with NA
all_data <- all_data %>%
  mutate(across(where(is.integer), ~na_if(., 9999)))

# define list of countries
countries <- unique(all_data$COUNTRY)

```


```{r, echo = F, results='asis'}
# determine unique variable names
vars <- c(
  # self-concept
  "SELFCON_baseline",
  "SELFCON_posttest",
  # personal interest
  "PINT_current",
  "PINT_posttest",
  # general self-efficacy
  "GENSELFEFF_current",
  "GENSELFEFF_posttest",
  # MATCHED task-specific self- efficacy 
  "EFFICACY_MATCHED_baseline",
  "EFFICACY_MATCHED_posttest"
)

# determine items that are summed up to factor
scales <- c(
  # self-concept
  paste0("SQA06", LETTERS[1:6],collapse = " + "),
  paste0("SQB01", LETTERS[1:6],collapse = " + "),
  # personal interest
  paste0("SQA14", LETTERS[1:3],collapse = " + "),
  paste0("SQB03", LETTERS[1:3],collapse = " + "),
  # general self-efficacy
  paste0("SQA15", LETTERS[1:5],collapse = " + "),
  paste0("SQB02", LETTERS[1:5],collapse = " + "),
  # MATCHED task-specific self- efficacy 
  paste0("SQA16", LETTERS[6:10],"2", collapse = " + "),
  paste0("SQB07C", LETTERS[1:5], collapse = " + ")
)


# combine to df for checking
df <- data.frame(vars, scales)
df$models <- paste(vars, "=~", scales)
```

Based on the result that measurement invariance did not hold when using data from all 8 countries, here the results are presented when systematically removing one country at a time.  

To determine measurement invariance (MI) for the questionnaire responses given by students, CFA was applied. More specifically, for each questionnaire scale, we first defined a CFA model where all items in the scale are loading on a single factor. All items were defined as being ordered categorical. 

> factor =~ item_1 + item_2 + ... + item_n  

For the multi-group CFA, the same model is fitted in all groups. To determine metric MI, a configural and a metric model were fitted and compared. The model fit incides and changes therein were summarised in a table.  

The outlined procedure was followed for each questionnaire scale of interest. The results are shown below.  

The tables below show the model comparison statistics and change in fit indices. If the change exceeded thresholds (i.e., **decrease in CFI of more than  -.02 and increase in RMSEA of more than .03**), this was highlighted in red. A separate table was created for the each possible removal of country.    


```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# debug
# vars <- vars[2]

for (c in 1:length(countries)) {
  
  # remove data from country
  stud <- subset(all_data, all_data$COUNTRY != countries[c])
  
  # loop over all variables
  for (v in 1:length(vars)) {
    
    # lavaan model formulation
    model <- paste(vars[v], "=~", scales[v])
    
    # configural invariance #
    
    # fit CFA to test for configural invariance
    config <- lavaan::cfa(model, ordered = T, data = stud, group = "COUNTRY")
    
    # metric invariance #
    
    metric <-lavaan::cfa(model, ordered = T, data = stud, group = "COUNTRY", group.equal = c("loadings"))
    
    # compare model fit
    comp <- compareFit(list(config, metric))
    
    tmp <- slot(comp, "nested")
    
    tmp <- tmp[!is.na(tmp$`Df diff`),]
    tmp$variable <- vars[v]
    
    tmp3 <- tmp[, c("variable",
                    "Chisq diff", "Df diff", "Pr(>Chisq)")]
    row.names(tmp3) <- NULL
    names(tmp3) <- c("variable", 
                     "chisq", "df", "pvalue")
    
    
    tmp <- slot(comp, "fit.diff")
    
    tmp$variable <- vars[v]
    tmp$model <- c("Δ_conf_metr")
    
    tmp4 <- tmp[, c("variable", 
                    "cfi", "cfi.scaled", "cfi.robust",
                    "tli", "tli.scaled", "tli.robust",
                    "rmsea", "rmsea.scaled", "rmsea.robust")]
    row.names(tmp4) <- NULL
    
    # merge 
    tmp <- merge(tmp3, tmp4, by = c("variable"))
    
    
    # combine all data in one output for extraction
    if (v == 1) {
      out <- tmp
    } else {
      out <- rbind(out, tmp)
    }
    
  }
  
  
  # define thresholds for highlighting
  col.red <- which(out$cfi < -.02 | out$rmsea > .03)
  
  # print summary table
  kbl(out, digits = 3, row.names = F,
      caption = paste0("Metric vs. configural model (", countries[c], " removed)")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    kableExtra::column_spec(5, bold = TRUE) %>%
    kableExtra::column_spec(11, bold = TRUE) %>%
    row_spec(col.red, color = red) %>%
    print()
  cat("\n\n")
  
  
}

```


