---
title: "Measurement invariance (MI): Pupil perspective on selected teaching-related constructs (selected 5 countries) using CFA model suggested by GTI authors"
author: "Stef Meliss"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
# empty work space
rm(list = ls())

# define directory
dir <- getwd()
dir <- gsub("/00_explore", "", dir)

# load libraries
library(kableExtra)
library(dplyr)
library(ggplot2)

library(mirt)
library(ggmirt)

library(plotly)

library(lavaan)
library(semPlot)
library(semptools)
library(semTools)

# load in functions
#devtools::source_url("https://github.com/stefaniemeliss/Global_Teaching_InSights/blob/main/functions.R?raw=TRUE")
source("C:/Users/stefanie.meliss/OneDrive - Ambition Institute/code/Global_Teaching_InSights/functions.R")

# read in data
all_data <- read.csv(file.path(dir, "data_raw", "GTI-Student-Data.csv"))

# replace all 9999 with NA
all_data <- all_data %>%
  mutate(across(where(is.integer), ~na_if(., 9999))) %>% # missing
  mutate(across(where(is.integer), ~na_if(., 9998))) %>% # multiple responses
  mutate(across(where(is.integer), ~na_if(., 9997))) # Illegible response

# recode items
all_data[,paste0("SQB11", LETTERS[c(1, 2, 3)])] <- 5 - all_data[,paste0("SQB11", LETTERS[c(1, 2, 3)])]

```

Previous results showed that when three countries are removed systematically, measurement invariance (MI) in the non-cognitive outcome measures can be established. However, there were three different possible combinations that achieved this outcome. This markdown document compares re-runs the measurement invariance test for all three data subsets for the student ratings of teaching-related constructs.   



# Contents  

[Shanghai, Japan & Madrid removed](#madrid)  
[Shanghai, Japan & Chile removed](#chile)  
[Shanghai, Japan & Mexico removed](#mexico)  


```{r, echo = F, results='asis'}
m_gti <- # model using items and factors as specified by the GTI team
  ' 
  f1 =~ SQB08A + SQB08B + SQB08C + SQB08D
  f2 =~ SQB08E + SQB08F + SQB08G + SQB08H
  f3 =~ SQB08I + SQB08J + SQB08K
  f4 =~ SQB09A + SQB09B + SQB09C + SQB09D
  f5 =~ SQB10A + SQB10B + SQB10C + SQB10D + SQB10E
  f6 =~ SQB11A + SQB11B + SQB11C
  f7 =~ SQB11F + SQB11G + SQB11I + SQB11J
  f8 =~ SQB12A + SQB12B + SQB12C
  f9 =~ SQB12D + SQB12E + SQB12F + SQB12G 
  f10 =~ SQB12H + SQB12I + SQB12J + SQB12K 
  f11 =~ SQB13A + SQB13B + SQB13C + SQB13D + SQB13E 
  f12 =~ SQB16A + SQB16B + SQB16C + SQB16D 
'

```



# Approach

To determine measurement invariance (MI) for the questionnaire responses given by students, CFA was applied. More specifically, for each questionnaire scale, we first defined a CFA model where all items in the scale are loading on a single factor. All items were defined as being ordered categorical. 

> factor =~ item_1 + item_2 + ... + item_n  

This model was first fitted on all available data across all countries, model fit indices were extracted and a path diagram was created.  

Next, we fitted the model to each country separately to extract model fit indices for each country. These are summarised in a table.  

For the multi-group CFA, the same model is fitted in all groups. To establish metric (or weak) MI,  the pattern of salient (non-zero) and non-salient (zero) loadings was compared across groups. This was done by extracting the p-values associated with each loading and binarising it through comparison against an alpha value of .05. In a next step, we checked whether  there is any variance in the binarised p values across countries for each item. If the variance was zero for each item, we can assume that the same pattern of salient and non-salient loadings occurs across countries.  

To determine MI, a configural, a metric and a scalar model were fitted and compared. The model fit indices and changes therein were summarised in a table.  

The outlined procedure was followed for each questionnaire scale of interest. The results are shown below.  

```{r working_chunk, echo=FALSE, eval=F}

# lavaan model formulation
model <- m_gti

# baseline model #

# fit CFA
baseline <-lavaan::cfa(model, ordered = T, data = stud) 

# put summary in object
fit_baseline <- summary(baseline, fit.measures = TRUE)

cat("##### Fitting the model to all available data \n\n")

cat("Model Test User Model::\n\n")

cat("\tTest Statistic:\t\t\t\t\t\t\t\t\t\t", round(fit_baseline$test$standard$stat,3),"\n")
cat("\tDegrees of freedom:\t\t\t\t\t\t\t\t\t", fit_baseline$test$standard$df,"\n")
cat("\tP-value (Chi-square):\t\t\t\t\t\t\t\t", round(fit_baseline$test$standard$pvalue,3),"\n\n")


cat("User Model versus Baseline Model:\n\n")

cat("\tComparative Fit Index (CFI):\t\t\t\t\t\t", round(fit_baseline$fit["cfi"],3),"\n")
cat("\tTucker-Lewis Index (TLI):\t\t\t\t\t\t\t", round(fit_baseline$fit["tli"],3),"\n")
cat("\tRoot Mean Square Error of Approximation (RMSEA):\t", round(fit_baseline$fit["rmsea"],3),"\n\n")



cat("The loadings of each item on the factor were plotted in a path diagram. The path diagram was computed pooling the data across all countries.")

cat("\n\n")

# plot path model with paramter estimates (i.e., loadings)
path_diag <- mark_sig(semPaths(baseline, "est", curvePivot = TRUE, thresholds = FALSE,  edge.label.cex = 1, title.cex = 1, reorder = F, sizeMan = 10, sizeLat = 14, intercepts = F, layout = "circle2", DoNotPlot = T), baseline)
plot(path_diag)

# extract relevant information from fit_baseline
loadings <- fit_baseline$pe[startsWith(fit_baseline$pe$lhs, "f") & startsWith(fit_baseline$pe$rhs, "SQB"), ]
loadings$group <- "all"


cat("The model was then fitted separately for each country. Model fit indices are included in the table below. Data for a country is **highlighted in blue if CFI or TLI are below .95 or if RMSEA is above .1**.\n\n")

# baseline model fit in each country #

countries <- unique(stud$COUNTRY)

df_conf <- data.frame(Country = countries,
                      Chi.square = NA,
                      Df = NA,
                      p.Value = NA,
                      CFI = NA,
                      TLI = NA,
                      RMSEA = NA)


for (c in 1:length(countries)) {
  
  # compute CFA in each country
  tmp_fit <-lavaan::cfa(model, ordered = T, data = stud[stud$COUNTRY == countries[c], ])
  
  # put summary in object
  tmp <- summary(tmp_fit, fit.measures = TRUE)
  
  # add to data frame
  df_conf$Chi.square[df_conf$Country == countries[c]] <- tmp$fit["chisq"]
  df_conf$Df[df_conf$Country == countries[c]] <- tmp$fit["df"]
  df_conf$p.Value[df_conf$Country == countries[c]] <- tmp$fit["pvalue"]
  df_conf$CFI[df_conf$Country == countries[c]] <- tmp$fit["cfi"]
  df_conf$TLI[df_conf$Country == countries[c]] <- tmp$fit["tli"]
  df_conf$RMSEA[df_conf$Country == countries[c]] <- tmp$fit["rmsea"]
  
}

# define thresholds for highlighting
col.cfi <- which(df_conf$CFI < .95)
col.tli <- which(df_conf$tli < .95)
col.rmsea <- which(df_conf$RMSEA > .1)

# print table
kbl(df_conf, digits = 3,
    caption = "Model fit in each country") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(col.cfi, bold = T, color = blue) %>%
  row_spec(col.tli, bold = T, color = blue) %>%
  row_spec(col.rmsea, bold = T, color = blue) %>%
  print()
cat("\n")

cat("##### Fitting the model for multigroup CFA \n\n")

# configural invariance #

# fit CFA to test for conigural invariance
config <- lavaan::cfa(model, ordered = T, data = stud, group = "COUNTRY")

# put summary in object
fit_config <- summary(config, fit.measures = TRUE)

# extract relevant information from fit_config
loadings_c <- fit_config$pe[startsWith(fit_config$pe$lhs, "f") & startsWith(fit_config$pe$rhs, "SQB"), ]

# add country information
loadings_c$group <- fit_config$data$group.label[loadings_c$group]
loadings_c$block <- NULL

# combine data from all countries with data from each country
loadings <- rbind(loadings, loadings_c)

# use relevant cols only
tmp3 <- loadings[, c("rhs", "group", "pvalue")]
tmp3$pvalue <- tmp3$pvalue < 0.05 # true if item loads significantly on factor

# reshape
tmp4 <- reshape(tmp3, idvar = "rhs", timevar = "group", direction = "wide")

# create a variable that checks whether the loading is significant across all countries
# this is done by computing the SD of the boolean variable pvalue per country
tmp4$sd_loadings_sig <- apply(tmp4[, -1], MARGIN = 1, FUN = sd, na.rm = T)

# check if configural invariance was achieved
if (sum(tmp4$sd_loadings_sig != 0, na.rm = T) == 0) {
  cat("Comparing the salient loadings across countries showed that the same set of items were associated with the latent factor across all countries.")
} else {
  cat("Comparing the salient loadings across countries showed that the same set of items were not associated with the latent factor across all countries.")
}

cat("\n\n")

# metric invariance #

metric <-lavaan::cfa(model, ordered = T, data = stud, group = "COUNTRY", group.equal = c("loadings"))

# compare model fit
comp <- compareFit(list(config, metric))

# save fit data
tmp <- slot(comp, "fit")

tmp$model <- c("config", "metric")

tmp2 <- tmp[, c("model",
                "chisq", "df", "pvalue",
                #"chisq.scaled", "df.scaled", "pvalue.scaled",
                "cfi", "cfi.scaled", "cfi.robust",
                "tli", "tli.scaled", "tli.robust",
                "rmsea", "rmsea.scaled", "rmsea.robust")]

row.names(tmp2) <- NULL

# define threshold
col.blue <- integer(0)
# if CFI drops by more than .02 or if RMSEA increases by more than .03
if (tmp2$cfi[1] < .95 | tmp2$tli[1] < .95 | tmp2$rmsea[1] > .1) {
  # colour row red
  col.blue <- 1
}

# get chi square model comparison etc
tmp <- slot(comp, "nested")

tmp <- tmp[!is.na(tmp$`Df diff`),]
tmp$model <- c("Δ_conf_metr")

tmp3 <- tmp[, c( "model",
                "Chisq diff", "Df diff", "Pr(>Chisq)")]
row.names(tmp3) <- NULL
names(tmp3) <- c("model",
                 "chisq", "df", "pvalue")

# change in model fit indices
tmp <- slot(comp, "fit.diff")

tmp$model <- c("Δ_conf_metr")


tmp4 <- tmp[, c("model",
                "cfi", "cfi.scaled", "cfi.robust",
                "tli", "tli.scaled", "tli.robust",
                "rmsea", "rmsea.scaled", "rmsea.robust")]
row.names(tmp4) <- NULL


# define thresholds for highlighting
col.red <- which(tmp4$cfi < -.02 | tmp4$rmsea > .03)

# merge 
tmp3 <- merge(tmp3, tmp4, by = c("model"))

# merge model data and model comparison data
tmp <- rbind(tmp2, tmp3)

# adjust row numbers after merging
if(length(col.red) != 0){
  col.red <- col.red + nrow(tmp2)
}

cat("Configural, metric and scalar invariance were modeled. The respective model fit indices are shown in the first three rows in the table below. If the configural model did not have good fit indices (i.e., **CFI or TLI are below .95 or if RMSEA is above .1** ), this is nighlighted in blue. The last two rows show the model comparison statistics and change in fit indices. If the change exceeded thresholds (i.e., **decrease in CFI of more than  -.02 and increase in RMSEA of more than .03**), this was highlighted in red. \n\n")


# print table
kbl(tmp, digits = 3,
    caption = "Model fit indices and changes therein using data from all countries") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  kableExtra::column_spec(5, bold = TRUE) %>%
  kableExtra::column_spec(11, bold = TRUE) %>%
  row_spec(col.blue, color = blue) %>%
  row_spec(col.red, color = red) %>%
  print()
cat("\n")

```


# Shanghai, Japan & Madrid removed {#madrid}

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define data input #

# countries to exclude
countries <- c("Shanghai", "Japan", "Madrid")

# remove data from country
stud <- all_data %>% 
  filter(!COUNTRY %in% countries)

<<working_chunk>>
```

# Shanghai, Japan & Chile removed {#chile}

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define data input #

# countries to exclude
countries <- c("Shanghai", "Japan", "Chile")

# remove data from country
stud <- all_data %>% 
  filter(!COUNTRY %in% countries)

<<working_chunk>>

```

# Shanghai, Japan & Mexico removed {#mexico}

```{r, echo = F, results='asis', fig.align='center', warning=FALSE}
# define data input #

# countries to exclude
countries <- c("Shanghai", "Japan", "Mexico")

# remove data from country
stud <- all_data %>% 
  filter(!COUNTRY %in% countries)

<<working_chunk>>

```

